Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-09 writeup/gz_hubble_data.tex
Updated caption and response for Figure 8. Closes #185.

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/z1_mu20_subplot2.pdf}
\caption{A larger version of the dark-outlined square in Figure~\ref{fig:f_vs_f}, containing
\ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have
surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. The orange bars represent the inner
80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower
and upper limits of the debiased values.}
\label{fig:f_vs_f_zoom}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/z1_mu20_subplot2.pdf}
\caption{A larger version of the dark-outlined square in Figure~\ref{fig:f_vs_f}, containing
\ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have
surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. The orange bars represent the inner
68\% (1$\sigma$) of the uncorrectable \ffeatures{} quantiles, which are used
to compute the limits on the range of debiased values.}
\label{fig:f_vs_f_zoom}
\end{figure}
